---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinywqg

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Apache license](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)
<!-- badges: end -->

shinywqg is a repository to run the 'B.C. Ambient Water Quality Guidelines' Shiny application. Guidelines are read directly from the BC Data Catalogue.

## Installation

Clone the repository from [GitHub](https://github.com/bcgov/shinywqg)

## Demonstration
```{r, eval=FALSE}
# install.packages("shiny")
shiny::shinyAppDir(".")
```

## Contribution

Please report any [issues](https://github.com/bcgov/shinywqg/issues).

[Pull requests](https://github.com/bcgov/shinywqg/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/bcgov/shinywqg/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
