---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinywqg

<!-- badges: start -->
[![img](https://img.shields.io/badge/Lifecycle-Maturing-007EC6)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)
[![R-CMD-check](https://github.com/poissonconsulting/dbflobr/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/dbflobr/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/dbflobr/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/dbflobr?branch=master)
[![Apache license](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)
<!-- badges: end -->

shinywqg is an R package to run the 'B.C. Ambient Water Quality Guidelines' Shiny application. 
Guidelines are determined based on information from the BC Data Catalogue.

The shiny application is also available at https://bcgov-env.shinyapps.io/bc_wqg/.

## Installation

To install the developmental version from [GitHub](https://github.com/bcgov/shinywqg)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("bcgov/shinywqg")
```

## Demonstration
```{r, eval=FALSE}
shinywqg::run_wqg_app()
```

## Contribution

Please report any [issues](https://github.com/bcgov/shinywqg/issues).

[Pull requests](https://github.com/bcgov/shinywqg/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/bcgov/shinywqg/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
